FictionEro - Data Cleaning

### 2024-02-16 analysis/1_cleaning.qmd
Add graph analysis

The majority of participants found it to be a "fun" experience. It is interesting to note that reports of "fun" were significantly associated with finding (some) stimuli arousing. Conversely, reporting "no feelings" was associated with finding the experiment "boring".

@@

### Structure

@@

```{r}
bait <- df |> 
  select(starts_with("BAIT_"), -BAIT_Duration)

@@

```{r}
m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=df)
m2 <- lavaan::cfa(
  "G =~ BAIT_5_ImitatingReality + BAIT_6_EnvironmentReal + BAIT_4_VideosIssues + BAIT_8_TextIssues + BAIT_3_VideosRealistic + BAIT_1_ImagesRealistic + BAIT_2_ImagesIssues + BAIT_7_TextRealistic", 
  data=df)

@@

@@

# Merge with data
scores <- lavaan::predict(m1) |> 
  as.data.frame() |> 
  data_rename(c("ML2"), c("BAIT_SEM")) |> 
  mutate(Participant = df$Participant) |>
  mutate(BAIT = rowMeans(select(bait, -contains("Videos")), na.rm = TRUE))

df <- full_join(df, scores[c("Participant", "BAIT_SEM", "BAIT")], by="Participant")
```

@@

```{r}
correlation::cor_test(scores, "BAIT_SEM", "BAIT") |> 
  plot() +
  ggside::geom_xsidedensity(aes(x=BAIT_SEM), color="grey", linewidth=1) +
  ggside::geom_ysidedensity(aes(y=BAIT), color="grey", linewidth=1) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .1) 
```

@@

@@

# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
m <- lm(BAIT_SEM ~ AI_Knowledge, data=df)
# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=dfsub, algorithm = "meanfield")
# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
display(parameters::parameters(m))

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  geom_jitter2(data=df, aes(y=BAIT_SEM), alpha=0.2, width=0.1) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT Score")
```

@@

```{r}
# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
m <- lm(BAIT_SEM ~ Sex / Age, data=df)
display(parameters::parameters(m))
```

@@

```{r}
glm(Feedback_LabelsIncorrect ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are Incorrect'")
```

```{r}
glm(Feedback_LabelsReversed ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are reversed'")
```

```{r}
glm(Feedback_CouldDiscriminate ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Easy to discriminate'")
```

```{r}
glm(Feedback_CouldNotDiscriminate ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Hard to discriminate'")
```

```{r}
glm(Feedback_Fun ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Fun'")
```

```{r}
glm(Feedback_Boring ~ BAIT_SEM * AI_Knowledge, 
    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Boring'")
```

>>>>

The majority of participants found the study to be a "fun" experience. Interstingly, reports of "fun" were significantly associated with finding at least some stimuli arousing. Conversely, reporting "no feelings" was associated with finding the experiment "boring".

@@

### Factor Analyis

@@

```{r}
bait <- df |> 
  select(starts_with("BAIT_"), -BAIT_Duration) |> 
  rename_with(function(x) gsub("BAIT_\\d_", "", x))

@@

```{r}
m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=bait)
m2 <- lavaan::cfa(
  "G =~ ImitatingReality + EnvironmentReal + VideosIssues + TextIssues + VideosRealistic + ImagesRealistic + ImagesIssues + TextRealistic", 
  data=bait)

@@

### Graph Analysis

Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.

#### Unique Variable Analysis (UVA)

Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network. Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).

```{r}
uva <- EGAnet::UVA(data = bait, cut.off = 0.3)
uva
uva$keep_remove
```

#### Networks

```{r}
#| fig-height: 20
#| fig-width: 12

ega <- list()
for(model in c("glasso", "TMFG")) {
  for(algo in c("walktrap", "louvain")) {
    for(type in c("ega", "ega.fit")) {  # "hierega"
      if(type=="ega.fit" & algo=="louvain") next  # Too slow
      ega[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
        data = bait,
        seed=123,
        model=model,
        algorithm=algo,
        EGA.type=type,
        type="resampling",
        plot.itemStability=FALSE,
        verbose=FALSE)
      }
   }
}

EGAnet::compare.EGA.plots(
  ega$glasso_walktrap_ega, ega$glasso_walktrap_ega.fit,
  ega$glasso_louvain_ega, ega$TMFG_louvain_ega,
  ega$TMFG_walktrap_ega, ega$TMFG_walktrap_ega.fit,
  labels=c("glasso_walktrap_ega", "glasso_walktrap_ega.fit",
           "glasso_louvain_ega", "TMFG_louvain_ega",
           "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit"),
                          rows=3,
  plot.all = FALSE)$all
```

#### Dimension Stability

Figures shows how often each variable is replicating in their empirical structure across bootstraps.

<!-- The summary statistics produced also relay this information as well as structural consistency. Structural consistency is defined as the extent to which each empirically derived dimension is exactly (i.e., identical variable composition) recovered from the replicate bootstrap samples (Christensen, Golino, & Silvia, 2020). In general, values of structural consistency and item stability greater than 0.70-0.75 reflect sufficient stability (Christensen & Golino, 2021). -->

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(ega, plot), nrow = 3)
```

#### Final Model

```{r}
ega <- ega$TMFG_walktrap_ega$EGA
plot(ega)

ega_scores <-  EGAnet::net.scores(bait, ega)$scores$std.scores |> 
  as.data.frame() |> 
  setNames(c("EGA1", "EGA2")) 
```

@@

# Merge with data
scores <- lavaan::predict(m1) |> 
  as.data.frame() |> 
  data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
  cbind(ega_scores) |> 
  mutate(Participant = df$Participant) |>
  mutate(BAIT = rowMeans(select(bait, -contains("Videos")), na.rm = TRUE))

df <- full_join(df, scores, by="Participant")
```

@@

```{r}
correlation::cor_test(scores, "BAIT_SEM2", "BAIT") |> 
  plot() +
  ggside::geom_xsidedensity(aes(x=BAIT_SEM2), color="grey", linewidth=1) +
  ggside::geom_ysidedensity(aes(y=BAIT), color="grey", linewidth=1) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .1) 
```

@@

```{r}
table <- correlation::correlation(scores) |> 
  summary()

@@

# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
m <- lm(BAIT ~ AI_Knowledge, data=df)
# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
display(parameters::parameters(m))

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  geom_jitter2(data=df, aes(y=BAIT), alpha=0.2, width=0.1) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT Score")
```

@@

```{r}
# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
m <- lm(BAIT ~ Sex / Age, data=df)
display(parameters::parameters(m))
```

@@

```{r}
glm(Feedback_LabelsIncorrect ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are Incorrect'")
```

```{r}
glm(Feedback_LabelsReversed ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are reversed'")
```

```{r}
glm(Feedback_CouldDiscriminate ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Easy to discriminate'")
```

```{r}
glm(Feedback_CouldNotDiscriminate ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Hard to discriminate'")
```

```{r}
glm(Feedback_Fun ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Fun'")
```

```{r}
glm(Feedback_Boring ~ BAIT * AI_Knowledge, 
    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Boring'")
```
